Methodology for Assessing the State of the Practice for Domain X

### 2020-04-20 StateOfPractice/Methodology/Methodology.tex
updated .bib, methodology file

- Pairwise Comparison Methodology needs to be described
- Downloaded OBS to record experiment sessions, will test it's capability
Describe experiments with users to assess usability, performance etc.

>>>>

- Pairwise Comparison Methodology needs to be described\\
- Downloaded OBS to record experiment sessions, will test it's capability\\
- Describe experiments with users to assess usability, performance etc.
